openarchaeoCollaboration

### 2021-03-12 analysis/paper.Rmd
Add quick analysis of issue usage

>>>>

```{r plot-gh_issues-histogram}
oarch %>% 
  unnest(gh_issues) %>% 
  drop_na(title) %>% 
  group_by(repo) %>% 
  summarise(n = n(), .groups = "drop") %>%
  ggplot(aes(x = n)) +
  geom_histogram(binwidth = 1) +
  labs(
    title = "Repository issues",
    caption = "Data: <https://open-archaeo.info> and the GitHub API",
    x = "Number of issues", y = "Number of repositories"
  )
```
